The Freeplay Sandbox: a Novel Methodology for the Evaluation of Social Robotics

### 2017-10-06 paper.tex
Update on Overleaf.

>>>>

We presented a set-up and data set of relatively unconstrained interaction between children and between a robot and a child. The set-up captures a rich set of multimodal streams which can be used to mine the social, verbal and non-verbal communication between two parties engaging in a relatively rich free play interaction. The data holds considerable promise for training social signal interpretation software, such as engagement interpretation or eye gaze reading. The dataset collected has sufficiently rich data and a wide range of multi-modal dimensions making it particularly suitable for Deep Learning of social signal processing algorithms. It also allow for very rich input to action selection mechanisms needed for autonomous robot behaviour. Future work will focus on using mining the data for patterns in free play, as per Parten's classification, and will attempt to extract social signals relevant to drive the interaction. Early results show that Deep Learning shows considerable promise for high-resolution tracking of eye gaze from the RGB video streams.
